\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-03-18 paper/main.tex
Added comment about bugsinpy
Reduced fontsize of code snippets

@@

\begin{lstlisting}[language=python]
def test_f():
  input_data = torch.randn(3, 4, 5, 6)
  scale = np.array([0.1, 0.2, 0.3, 0.4])
  zero_point = torch.tensor([1, 2, 3, 4], dtype=torch.int32)
  axis = 1
  quant_min = 0
  quant_max = 255
  with pytest.raises(RuntimeError) as e_info:
      output = torch.fake_quantize_per_channel_affine(input_data, torch.from_numpy(scale), zero_point, axis, quant_min, quant_max)
  print(f'{e_info.type.__name__}: {e_info.value}')
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$> git clone git@github.com:ncsu-swat/bugsindlls.git
$> cd bugsindlls
$> export PATH=$PATH:`pwd`/framework
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$> run-test --library-name pytorch --bug-id 120903
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
... 
Versions of relevant libraries:
[pip3] numpy==1.26.4
[pip3] torch==2.2.0+cpu
[conda] torch                     2.2.0+cpu                pypi_0    pypi
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
rootdir: /home/mnaziri/Documents/DL_Testing/dnnbugs/pytorch/issue_120903
collected 1 item

@@

\begin{lstlisting}[language=bash,keywords={}]
$> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
$> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
...  
(*@\textbf{[Reproducing the bug]}@*)
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
...
IndexError: list index out of range
====== 1 passed in 1.09s ======
...

>>>>

\Fix{Need to add text regarding differentiating the tool from BugsInPy}

@@

\begin{lstlisting}[language=python,basicstyle=\small,]
def test_f():
  input_data = torch.randn(3, 4, 5, 6)
  scale = np.array([0.1, 0.2, 0.3, 0.4])
  zero_point = torch.tensor([1, 2, 3, 4], dtype=torch.int32)
  axis = 1
  quant_min = 0
  quant_max = 255
  with pytest.raises(RuntimeError) as e_info:
      output = torch.fake_quantize_per_channel_affine(input_data, torch.from_numpy(scale), zero_point, axis, quant_min, quant_max)
  print(f'{e_info.type.__name__}: {e_info.value}')
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,]
$> git clone git@github.com:ncsu-swat/bugsindlls.git
$> cd bugsindlls
$> export PATH=$PATH:`pwd`/framework
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,]
$> run-test --library-name pytorch --bug-id 120903
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,]
... 
Versions of relevant libraries:
[pip3] numpy==1.26.4
[pip3] torch==2.2.0+cpu
[conda] torch                     2.2.0+cpu                pypi_0    pypi
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.2.0, pluggy-1.5.0
rootdir: /home/mnaziri/Documents/DL_Testing/dnnbugs/pytorch/issue_120903
collected 1 item

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
$> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
...  
(*@\textbf{[Reproducing the bug]}@*)
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
...
IndexError: list index out of range
====== 1 passed in 1.09s ======
...
